A hybrid approach for news recommender system using optimization methods

### 2021-01-09 paper/paper.tex
added popularity based table

    \keywords{recommender systems \and content-based recommender \and collaborative recommender \and optimizations}

@@

                \emph{user\_id} & \emph{item\_id} \\\midrule
                10 & 1  \\
                10 & 2  \\
                23 & 1  \\
                23 & 3  \\
                23 & 2  \\
                38 & 3  \\
                38 & 1  \\
                \vdots & \vdots  \\\bottomrule
            \end{tabular}
            \caption{news shows}
            \label{tab:shows}
        }
        \hfill
        \parbox{.45\textwidth}{
            \centering
            \begin{tabular}{ccc}
                \toprule

                \emph{user\_id} & \emph{item\_id} \\\midrule
                10 & 1  \\
                10 & 2  \\
                23 & 1  \\
                38 & 3  \\
                \vdots & \vdots  \\\bottomrule
            \end{tabular}
            \caption{news views}
            \label{tab:views}
            }
    \end{table}

@@

@@

    We are able to aggreage number of comments and emotions to measure popularity.

    For measuring news item popularity views \& show can be aggregated from tables (cite tables) into:

@@

            \emph{item\_id} & \emph{date} & \emph{source\_id} & \emph{shows}                                                               & \emph{views}                                                 \\\midrule

        1 & 2021-01-08 22:08:39 & 9  & 1043 & 231        \\
        2 & 2021-01-09 10:28:58 & 5  & 828 & 478  \\
        3 & 2021-01-09 14:20:34 & 12 & 163 & 25 \\
        \vdots & \vdots & \vdots & \vdots & \vdots \\\bottomrule

@@

>>>>

    \keywords{hybrid recommender systems \and content-based recommender \and collaborative recommender \and optimizations}

@@

                \emph{user\_id} & \emph{item\_id} \\\midrule
                10 & 1  \\
                10 & 2  \\
                23 & 1  \\
                23 & 3  \\
                23 & 2  \\
                38 & 3  \\
                38 & 1  \\
                \vdots & \vdots  \\\bottomrule
            \end{tabular}
            \caption{news shows}
            \label{tab:show}
        }
        \hfill
        \parbox{.45\textwidth}{
            \centering
            \begin{tabular}{ccc}
                \toprule

                \emph{user\_id} & \emph{item\_id} \\\midrule
                10 & 1  \\
                10 & 2  \\
                23 & 1  \\
                38 & 3  \\
                \vdots & \vdots  \\\bottomrule
            \end{tabular}
            \caption{news views}
            \label{tab:view}
            }
    \end{table}

@@

    \subsection{Collaborative filtering recommendation}

    For collaborative filtering recommendation we should have something known as user-item matrix which may be formed from user activity from tables (cite tables)

@@

    For measuring news item popularity following data can be aggregated: \hyperref[tab:show]{shows}, \hyperref[tab:view]{views}, \hyperref[tab:emotion]{emotions}, \hyperref[tab:comment]{comments}.

@@

            \emph{item\_id} & \emph{shows\_num} & \emph{views\_num} & \emph{emotions\_num} & \emph{comments\_num} \\\midrule

            1 &  1043 & 231 & 52 & 7  \\
            2 &  828 & 478 & 78 & 11 \\
            3 &  163 & 25 & 5 & 0    \\
            \vdots & \vdots & \vdots & \vdots & \vdots \\\bottomrule

@@

        \caption{aggregated popularity data}
        \label{tab:popularity}
    \end{table}
